Share Buyback and Equity Issue Anomalies Revisited: Interactive Tool

### 2016-02-16 index.Rmd
tool update

---
title: "Share Buyback and Equity Issue Anomalies Revisited: Interactive Tool"
author: "[Theodoros Evgeniou](http://faculty.insead.edu/theodoros-evgeniou/), [Enric Junque de Fortuny](ciri.be/), [Nick Nassuphis](https://www.linkedin.com/in/nick-nassuphis-8029372), and [Theo Vermaelen](http://faculty.insead.edu/theo-vermaelen/)"
output:  
  html_document:
    fig_width: 6
    fig_height: 2.5
    fig_align: center
runtime: shiny
---

```{r, eval=TRUE, echo = FALSE}
#load("bb_issuersALL.Rdata")
load("bb_issuersTOOL.Rdata")

#library(googleVis)
#library("shiny")
#library("reshape2")  
#library("ggplot2")
# Why are these not found when deployed?!
library("stringr")
library("RcppArmadillo")
library("gtools")
library("timeDate")
source("lib/lib_helpers_shiny.R")
source("lib/Paper_global_parameters.R")
source("lib/heatmapOutput.R")
source("lib/plots.R")

DATASET_INI = BUYBACK_DATA$DATASET
DATASET_INI$SDC = as.data.frame(DATASET_INI$SDC)
```

@@

This is an interactive tool for the article [Share Buyback and Equity Issue Anomalies Revisited](). Users can explore the effects of various parameters as well as data filtering choices. For any given choices, users can generate and download a new **customized pdf version of the paper** by clicking the button below at any time. Note that it may take a couple of minutes to create and download the new paper.
<br>
<br>

@@

  list(
    returns_by_event_monthly = DATASET_INI$returns_by_event_monthly[,useonly_report],
    DatesMonth = DATASET_INI$DatesMonth[,useonly_report],
    SDC = DATASET_INI$SDC[useonly_report,]
    #returns_by_event_monthly = DATASET_INI$returns_by_event_monthly,
    #DatesMonth = DATASET_INI$DatesMonth,
    #SDC = DATASET_INI$SDC
  )
})
```

@@

```{r, eval=TRUE, echo = FALSE}
acceptaple_features = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index","Industry", "Market.Cap",          "Percent.Shares", "Purpose.Code","Source.of.funds","Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio", "Year")

fluidPage(
  selectInput("characteristic", "Select Firm Characteristic:", choices = acceptaple_features,selected = acceptaple_features[1]),
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Histogram",
                         renderPlot({
                           feature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic)]]
                           feature = feature[!is.na(feature)]
                           if (!is.numeric(feature))
                             feature = 1
                           hist(feature, density = 100, breaks = 100)
                         })),
                tabPanel("Summary Statistics",
                         renderDataTable({
                           feature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic)]]
                           #feature = feature[!is.na(feature)]
                           if (length(unique(feature)) > 20 & is.numeric(feature)){
                             res = t(as.matrix(summary(feature)))
                             colnames(res) <- c("Minimum", "1st Quantile", "Median", "Mean", "3rd Quantile", "Max")
                           }
                           if (is.character(feature) | length(unique(feature)) <= 20){
                             tmp = sort(table(feature), decreasing = TRUE)
                             res = t(as.matrix(tmp))
                           }
                           as.data.frame(res)
                           #m1<-gvisTable(show_data,options=list(showRowNumber=TRUE,width=1220, height=min(400,27*(nrow(show_data)+1)),allowHTML=TRUE,page='disable'))
                           #print(m1,'chart')
                         })
                )
    ),style='width: 100%;'))
```

@@

feature_IRATStable_industry <- reactive({
  useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
  res = round(cbind(
    car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly)$results,
    car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  as.data.frame(res)
})

feature_CALtable_industry <- reactive({
  useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
  res = round(cbind(
    calendar_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly)$results,
    calendar_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
  as.data.frame(res)
})

fluidPage(
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
                         renderTable({
                           feature_IRATStable_industry()
                         })),
                tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
                         renderTable({
                           feature_CALtable_industry()
                         }))    
    ),style='width: 100%;'))
```

@@

feature_IRATStable <- reactive({
  thesign = ifelse(input$characteristic_irats_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
  High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
  res = round(cbind(
    car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
    car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  as.data.frame(res)
})

feature_CALtable <- reactive({
  thesign = ifelse(input$characteristic_irats_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
  High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
  res = round(cbind(
    calendar_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
    calendar_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
  as.data.frame(res)
})

@@

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
                         renderTable({
                           feature_IRATStable()
                         })),
                tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
                         renderTable({
                           feature_CALtable()
                         })),
                tabPanel("Cumulative Abnormal Returns,High, 12m hold",
                         renderDygraph({
                           pnl_plot_interactive(High_feature_Hedged_react())
                         })),
                tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
                         renderDygraph({
                           pnl_plot_interactive(Low_feature_Hedged_react())
                         })),
                tabPanel("Monthly and Yearly Returns, High, 12m hold",
                         renderUI({
                           renderHeatmapX(pnl_matrix(High_feature_Hedged_react()))
                         })),
                tabPanel("Monthly and Yearly Returns, Low, 12m hold",
                         renderUI({
                           renderHeatmapX(pnl_matrix(Low_feature_Hedged_react()))
                         }))
    ),style='width: 100%;'))
```

@@

feature_IRATStable_index <- reactive({
  thefeature = Index_Score_rect()
  High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  res = round(cbind(
    car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
    car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  res
})

feature_CALtable_index <- reactive({
  thefeature = Index_Score_rect()
  High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  res = round(cbind(
    calendar_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
    calendar_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
  res
})

@@

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
                         renderTable({
                           feature_IRATStable_index()
                         })),
                tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
                         renderTable({
                           feature_CALtable_index()
                         })),
                tabPanel("Histogram of the New Index",
                         renderPlot({
                           feature = Index_Score_rect()
                           feature = feature[!is.na(feature)]
                           if (!is.numeric(feature))
                             feature = 1
                           hist(feature, density = 100, breaks = 100)
                         })),
                tabPanel("Cumulative Abnormal Returns,High, 12m hold",
                         renderDygraph({
                           pnl_plot_interactive(High_feature_Hedged_react_index())
                         })),
                tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
                         renderDygraph({
                           pnl_plot_interactive(Low_feature_Hedged_react_index())
                         })),
                tabPanel("Monthly and Yearly Returns, High, 12m hold",
                         renderUI({
                           renderHeatmapX(pnl_matrix(High_feature_Hedged_react_index()))
                         })),
                tabPanel("Monthly and Yearly Returns, Low, 12m hold",
                         renderUI({
                           renderHeatmapX(pnl_matrix(Low_feature_Hedged_react_index()))
                         }))
    ),style='width: 100%;'))
```

>>>>

---
title: "Share Buyback and Equity Issue Anomalies Revisited: Interactive Tool"
author: "[Theodoros Evgeniou](http://faculty.insead.edu/theodoros-evgeniou/), [Enric Junque de Fortuny](http://ciri.be/), [Nick Nassuphis](https://www.linkedin.com/in/nick-nassuphis-8029372), and [Theo Vermaelen](http://faculty.insead.edu/theo-vermaelen/)"
output:  
 html_document:
 fig_width: 6
 fig_height: 2.5
 fig_align: center
 in_header: header.html
 runtime: shiny
runtime: shiny
---

```{r, eval=TRUE, echo = FALSE,message=FALSE}
# rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
# source("create_tool_data.R")
load("bb_issuersTOOL.Rdata")
#load("tmpfiles/bb_issuersALL.Rdata")

#library(googleVis)
#library("shiny")
#library("reshape2")  
#library("ggplot2")
# Why are these not found when deployed?!
library("shiny") 
library("shinysky") #  devtools::install_github("AnalytixWare/ShinySky")

library("stringr")
library("RcppArmadillo")
library("gtools")
library("timeDate")
source("lib/lib_helpers_shiny.R")
source("lib/Paper_global_parameters.R")
source("lib/heatmapOutput.R")
source("lib/plots.R")
source("report_helpers.R")

DATASET_INI = BUYBACK_DATA$DATASET
DATASET_INI$SDC = as.data.frame(DATASET_INI$SDC)

if(0) {
  CACHE <- car_table_cache(DATASET_INI$returns_by_event_monthly,
                           DATASET_INI$SDC$Event.Date,Risk_Factors_Monthly,formula_used = five_factor_model)
  save("CACHE",file = "cache.Rdata")
}else {
  load("cache.Rdata")  
}
report_months_cal = c(as.numeric(reported_times[1:(length(reported_times)-1)]),1)

@@

This is an interactive tool for the article [Share Buyback and Equity Issue Anomalies Revisited](http://tevgeniou.github.io/BuybacksIssuers/). Users can explore the effects of various parameters as well as data filtering choices. For any given choices, users can generate and download a new **customized pdf version of the paper** by clicking the button below at any time.

**Note that it takes a few minutes (possibly five) to create and download the new paper - work in progress.**

@@

  list(
    returns_by_event_monthly = DATASET_INI$returns_by_event_monthly[,useonly_report],
    DatesMonth = DATASET_INI$DatesMonth[,useonly_report],
    SDC = DATASET_INI$SDC[useonly_report,],
    subset = useonly_report
    #returns_by_event_monthly = DATASET_INI$returns_by_event_monthly,
    #DatesMonth = DATASET_INI$DatesMonth,
    #SDC = DATASET_INI$SDC
  )
})
```

@@

```{r, eval=TRUE, echo = FALSE}
acceptaple_features = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index","Industry", "Market.Cap",          "Percent.Shares", "Purpose.Code","Source.of.funds","Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio")

fluidPage(
  selectInput("characteristic", "Select Firm Characteristic:", choices = acceptaple_features,selected = acceptaple_features[1]),
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Histogram",
                         busyIndicator("Please wait while we load the data for you... This shouldn't take more than a few seconds...",wait = 0),
                         renderPlot({
                           feature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic)]]
                           feature = feature[!is.na(feature)]
                           if (!is.numeric(feature))
                             feature = 1
                           hist(feature, density = 100, breaks = 100)
                         })),
                tabPanel("Summary Statistics",
                         renderDataTable({
                           feature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic)]]
                           #feature = feature[!is.na(feature)]
                           if (length(unique(feature)) > 20 & is.numeric(feature)){
                             res = t(as.matrix(summary(feature)))
                             colnames(res) <- c("Minimum", "1st Quantile", "Median", "Mean", "3rd Quantile", "Max")
                           }
                           if (is.character(feature) | length(unique(feature)) <= 20){
                             tmp = sort(table(feature), decreasing = TRUE)
                             res = t(as.matrix(tmp))
                           }
                           as.data.frame(res)
                           #m1<-gvisTable(show_data,options=list(showRowNumber=TRUE,width=1220, height=min(400,27*(nrow(show_data)+1)),allowHTML=TRUE,page='disable'))
                           #print(m1,'chart')
                         })
                )
    ),
    style='width: 100%;'))
```

@@

feature_IRATStable_industry <- reactive({
  useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
  res = round(cbind(
    #car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly)$results,
    #car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly)$results
    car_table_cached(CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued)$results,
    car_table_cached(CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  as.data.frame(res)
})

feature_CALtable_industry <- reactive({
  useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
  res = round(cbind(
    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly,report_months_cal)$results,
    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly,report_months_cal)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
  as.data.frame(res)
})

fluidPage(
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderTable({
                           feature_IRATStable_industry()
                         })),
                tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderTable({
                           feature_CALtable_industry()
                         }))    
    ),style='width: 100%;'))
```

@@

feature_IRATStable <- reactive({
  thesign = ifelse(input$characteristic_irats_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
  High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
  res = round(cbind(
    #car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
    #car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
    car_table_cached(CACHE,Low_feature_events)$results,
    car_table_cached(CACHE,High_feature_events)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  as.data.frame(res)
})

feature_CALtable <- reactive({
  thesign = ifelse(input$characteristic_irats_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
  High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
  res = round(cbind(
    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly,report_months_cal)$results,
    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly,report_months_cal)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
  as.data.frame(res)
})

@@

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderTable({
                           feature_IRATStable()
                         })),
                tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderTable({
                           feature_CALtable()
                         })),
                tabPanel("Cumulative Abnormal Returns,High, 12m hold",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderDygraph({
                           pnl_plot_interactive(High_feature_Hedged_react())
                         })),
                tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderDygraph({
                           pnl_plot_interactive(Low_feature_Hedged_react())
                         })),
                tabPanel("Monthly and Yearly Returns, High, 12m hold",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderUI({
                           renderHeatmapX(pnl_matrix(High_feature_Hedged_react()))
                         })),
                tabPanel("Monthly and Yearly Returns, Low, 12m hold",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderUI({
                           renderHeatmapX(pnl_matrix(Low_feature_Hedged_react()))
                         }))
    ),style='width: 100%;'))
```

@@

feature_IRATStable_index <- reactive({
  thefeature = Index_Score_rect()
  High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  res = round(cbind(
    #car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
    #car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
    car_table_cached(CACHE,Low_feature_events)$results,
    car_table_cached(CACHE,High_feature_events)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  res
})

feature_CALtable_index <- reactive({
  thefeature = Index_Score_rect()
  High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  res = round(cbind(
    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly,report_months_cal)$results,
    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly,report_months_cal)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
  res
})

@@

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderTable({
                           feature_IRATStable_index()
                         })),
                tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderTable({
                           feature_CALtable_index()
                         })),
                tabPanel("Histogram of the New Index",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderPlot({
                           feature = Index_Score_rect()
                           feature = feature[!is.na(feature)]
                           if (!is.numeric(feature))
                             feature = 1
                           hist(feature, density = 100, breaks = 100)
                         })),
                tabPanel("Cumulative Abnormal Returns,High, 12m hold",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderDygraph({
                           pnl_plot_interactive(High_feature_Hedged_react_index())
                         })),
                tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderDygraph({
                           pnl_plot_interactive(Low_feature_Hedged_react_index())
                         })),
                tabPanel("Monthly and Yearly Returns, High, 12m hold",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderUI({
                           renderHeatmapX(pnl_matrix(High_feature_Hedged_react_index()))
                         })),
                tabPanel("Monthly and Yearly Returns, Low, 12m hold",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderUI({
                           renderHeatmapX(pnl_matrix(Low_feature_Hedged_react_index()))
                         }))
    ),style='width: 100%;'))
```
